\textsc{LiveRec}: Framing Debug Protocols to Hotwire Probes

### 2023-09-28 paper/paper.tex
Figures

\section{Framing Debug Protocols}

@@

\begin{figure}[h]
  \centering
  \begin{minipage}{0.25\textwidth}
    \centering
    \begin{lstlisting}[language=C]
//foo(3)
int foo(int n) {
  int i = 0;
  while (i < n) {
    i++;
  }
  return i;
}
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.7\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth]{img/stackrecording_chain.png}
  \end{minipage}
  \caption{Stack Recording Example}
  \label{fig:stack-recording}
\end{figure}
%vRozen. The layout seems a bit off.
%vRozen. I propose merging Figure 3 and Table 1 into a single figure, the tabularx version below.

\begin{table}[t]
  \centering
  \includegraphics[width=\textwidth]{img/matrix.pdf}
  \caption{Tracking variable values across time and space}
\end{table}

%vRozen: Perhaps removing the time/space arrows would be better. it seems a bit cluttered
%vRozen: Perhaps we can still add boxes around the stack recordings to make it more similar to figure 4. It gives the feeling of having data structures, not just values.
\begin{figure}
  \centering
  \large  
  \hspace{8pt} \color{darkgray} \textsf{\textbf{time}}  \color{black} $\rightarrow$ \raggedright
  \vspace{2pt}

  \rotatebox{90}{$\leftarrow$ \color{darkgray} \textsf{\textbf{space} \color{black}}}
  \small
  \begin{tabularx}{0.94\textwidth}{ l @{\hspace{4pt}} l @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} l}  
  \toprule  
  &
  &
  \textbf{$t_1$}&
  \textbf{$t_2$}&
  \textbf{$t_3$}&
  \textbf{$t_4$}&
  \textbf{$t_5$}&
  \textbf{$t_6$}&
  \textbf{$t_7$}&
  \textbf{$t_8$}&
  \textbf{$t_9$}\\
  \midrule
  &
  &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} &
  \iC{n; i} \\
  \midrule
  1 & \iC{//foo(3)}\\
  2 & \iC{int foo(int n)\{} \\
  3 & \hspace{8pt}~\iC{int i = 0;}
  & \iC{3; _} \\  
  4 & \hspace{8pt}~\iC{while(i < n)\{} 
  &
  & \iC{3; 0}
  &
  & \iC{3; 1}
  & 
  & \iC{3; 2}\\
  5 & \hspace{16pt}~\iC{i++;}
  &
  &
  & \iC{3; 0}; 
  &
  & \iC{3; 1}\\
  6 & \hspace{8pt}~\iC{\}}\\
  7 & \hspace{8pt}~\iC{return i;}
  &
  &
  &
  &
  &
  &
  &
  &
  \iC{3; 3}\\
  8 & \iC{\}}
    &
  &
  &
  &
  &
  &
  &
  &
  &
  \iC{return 3}\\
  \bottomrule
  \end{tabularx}
  \caption{Tracking variable values across time and space}
\end{figure}

>>>>

\section{Framing Debug Protocols}
\label{sec:stack-recording}

@@

\begin{figure}[h]
  \centering
  \begin{minipage}{0.25\textwidth}
    \centering
    \begin{lstlisting}[language=C]
//@foo(3)
int foo(int n) {
  int i = 0;
  while (i < n) {
    i++;
  }
  return i;
}
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}{0.7\textwidth}
    \centering
    \includegraphics[width=0.8\linewidth]{img/stackrecording_chain.png}
  \end{minipage}
  \caption{Stack Recording Example}
  \label{fig:stack-recording}
\end{figure}
%vRozen. The layout seems a bit off.
%vRozen. I propose merging Figure 3 and Table 1 into a single figure, the tabularx version below.

% \begin{table}[t]
%   \centering
%   \includegraphics[width=\textwidth]{img/matrix.pdf}
%   \caption{Tracking variable values across time and space}
% \end{table}

%vRozen: Perhaps removing the time/space arrows would be better. it seems a bit cluttered
%vRozen: Perhaps we can still add boxes around the stack recordings to make it more similar to figure 4. It gives the feeling of having data structures, not just values.
\begin{figure}
  \centering
  \small
  \begin{tabularx}{0.94\textwidth}{ l @{\hspace{4pt}} l @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} X @{\hspace{4pt}} l}  
  \toprule  
  & \textsf{\textbf{time}} $\rightarrow$
  &
  \textbf{$t_1$}&
  \textbf{$t_2$}&
  \textbf{$t_3$}&
  \textbf{$t_4$}&
  \textbf{$t_5$}&
  \textbf{$t_6$}&
  \textbf{$t_7$}&
  \textbf{$t_8$}&
  \textbf{$t_9$}\\
  \midrule
  1 & \iC{//foo(3)}\\
  2 & \iC{int foo(int n)\{} \\
  3 & \hspace{8pt}~\iC{int i = 0;}
  & \iC{n=3} \\  
  4 & \hspace{8pt}~\iC{while(i < n)\{} 
  &
  & \iC{n=3; i=0}
  &
  & \iC{n=3; i=1}
  & 
  & \iC{n=3; i=2}\\
  5 & \hspace{16pt}~\iC{i++;}
  &
  &
  & \iC{n=3; i=0}; 
  &
  & \iC{n=3; i=1}\\
  6 & \hspace{8pt}~\iC{\}}\\
  7 & \hspace{8pt}~\iC{return i;}
  &
  &
  &
  &
  &
  &
  &
  &
  \iC{n=3; n=3}\\
  8 & \iC{\}}
    &
  &
  &
  &
  &
  &
  &
  &
  &
  \iC{return 3}\\
  \bottomrule
  \end{tabularx}
  \caption{Tracking variable values across time and space (= source code)}
\end{figure}
